Democracy, Public Support, and Measurement Uncertainty

### 2021-06-09 paper/dcpo_demsupport.Rmd
plot code revised

supdem <- read.csv(here("data", "Support_democracy_ajps.csv"))
v_dem <- read.csv(here("data", "vdem15.csv"))    ######????????? why we need this one? for graph?  in the following analysis, we never use v_dem
sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))

@@

```{r cls-uncertainAJPSfull, eval=FALSE}
result_clsUncertainFull <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r dcpo-uncertainAJPSfull, eval=FALSE}
result_dcpoUncertainFull <- map(ls_mod_ajpsDCPO, function(aMod){ # reading a model
  result <- map(dcpo_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", eval=FALSE}

df_plot <- df_result_dcpoMeanAJPS[[1]] %>% 
  mutate(model = "DCPO\n (Point Estimates)")

df_plot <- df_result_dcpoAJPS[[1]] %>%
  mutate(model = "DCPO\n (w. Uncertainty)") %>%
  rename(std.error = se) %>%
  bind_rows(df_plot)

plot_pooled <- filter(df_plot, model != "Claassen 2019") %>% 
  dwplot(by_2sd = FALSE) %>%
  relabel_predictors(
    c(
      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
      `plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
      `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
      `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
      `plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
      `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t-1)",
      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t-1)",
      `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t-1)",
      `plm::lag(Region_libdem, 1)` = "Regional democracy(t-1)",
      `plm::lag(Libdem_regUN, 1)` = "Regional democracy(t-1)",
      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
      `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t-1)",
      `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t-1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("DV: Liberal Democracy (Vdem)") +
  xlab("Coefficient Estimate") +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank()
  )

df_plot <- df_result_dcpoMeanAJPS[[2]] %>% 
  mutate(model = "DCPO\n (Point Estimates)")

df_plot <- df_result_dcpoAJPS[[2]] %>%
  mutate(model = "DCPO\n (w. Uncertainty)") %>%
  rename(std.error = se) %>%
  bind_rows(df_plot)

plot_pooled2 <- filter(df_plot, model != "Claassen 2019") %>% 
  dwplot(by_2sd = FALSE) %>%
  relabel_predictors(
    c(
      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
      `plm::lag(theta_dem, 1)` = "Mood Democracy(t-1)",
      `plm::lag(theta_aut, 1)` = "Mood Autocracy(t-1)",
      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t-1)",
      `plm::lag(Region_libdem, 1)` = "Regional democracy(t-1)",
      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t-1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("DV: Liberal Democracy (Vdem)") +
  xlab("Coefficient Estimate") +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank()
  )

gridExtra::grid.arrange(plot_pooled,plot_pooled2, ncol = 2)
```

@@

saveRDS(result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
```

@@

```{r cls-uncertainAPSRfull, eval=FALSE}
result_clsFullUncertainAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(cls_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

saveRDS(result_clsFullUncertainAPSR, file = here::here("output", "estimates_clsFullUncertainAPSR.RDS"))
```

@@

```{r dcpo-uncertainAPSRfull, eval=FALSE}
result_dcpoUncertainAPSR <- map(ls_mod_apsrDCPO, function(aMod){ # reading a model
  result <- map(dcpo_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoUncertainAPSR.RDS"))
```

@@

```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10, eval=FALSE}

result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
result_dcpoAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$pooled1[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$fd1[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$pooled2[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd2 <- bind_rows(
  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$fd2[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$`pooled-regime1`[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$`fd-regime1`[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_ecmReg2 <- bind_rows(
  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$`pooled-regime2`[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg2 <- bind_rows(
  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$`fd-regime2`[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

@@

```{r num-cls2020a, results='asis', eval = TRUE}
tb_result_cls <- map(result_cls, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-cls2020aUncertain, results='asis', eval = TRUE}
tb_result_clsUncertain <- map(result_clsUncertain, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-cls2020aDCPO, results='asis', eval = TRUE}
tb_result_DCPO <- map(result_dcpoUncertain, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-cls2020b, results='asis', eval = TRUE}
tb_result_clsAPSR <- map(result_clsAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@

```{r num-cls2020bUncertain, results='asis', eval = TRUE}
tb_result_clsUncertainAPSR <- map(result_clsUncertainAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@

```{r num-cls2020bDCPO, results='asis', eval = TRUE}
tb_result_dcpoAPSR <- map(result_dcpoAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@

```{r plot-fullpackAJPS, fig.cap= "The Effect of Public Support on Democracy", fig.width=7.5, fig.height=10}

@@

```{r plot-fullpackAJPSfull, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7}

@@

```{r plot-fullpackAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}

load(here::here("output", "estimates_dcpoAPSR.RDS"))

df_plot <- df_result_dcpoMeanAPSR[[1]] %>% 
  mutate(model = "DCPO\n (Point Estimates)")

df_plot <- df_result_dcpoAPSR[[1]] %>%
  mutate(model = "DCPO\n (w. Uncertainty)") %>%
  rename(std.error = se) %>%
  bind_rows(df_plot)

plot_pooled <- filter(df_plot, model != "Claassen 2019") %>% 
  dwplot(by_2sd = FALSE) %>%
  relabel_predictors(
    c(
      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
      `plm::lag(mdprgdp_grwth, 1)` = "Corruption (Difference)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("DV: Liberal Democracy (Vdem)") +
  xlab("Coefficient Estimate") +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank()
  )

df_plot <- df_result_dcpoMeanAPSR[[2]] %>% 
  mutate(model = "DCPO\n (Point Estimates)")

df_plot <- df_result_dcpoAPSR[[2]] %>%
  mutate(model = "DCPO\n (w. Uncertainty)") %>%
  rename(std.error = se) %>%
  bind_rows(df_plot)

plot_pooled2 <- filter(df_plot, model != "Claassen 2019") %>% 
  dwplot(by_2sd = FALSE) %>%
  relabel_predictors(
    c(
      `plm::lag(theta, 1:2)1` = "Democracy Mood(t-1)",
      `plm::lag(theta, 1:2)2` = "Democracy Mood(t-2)",
      `diff(Vdem_libdem_z, lag = 1)` = "Liberal Democracy (Diff)",
      `plm::lag(Vdem_libdem_z, 1)` = "Liberal Democracy (t-1)",
      `diff(lg_imp_mdpgdp, lag = 1)` = "Log GDP per capita(Diff)", 
      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t-1)",
      `diff(cpi_sd, lag = 1)` = "Corruption (Difference)",
      `plm::lag(cpi_sd, 1)` = "Corruption (t-1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("DV: Liberal Democracy (Vdem)") +
  xlab("Coefficient Estimate") +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank()
  )

gridExtra::grid.arrange(plot_pooled,plot_pooled2, ncol = 2)
```

```{r plot-fullpackAPSRfull, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}

>>>>

supdem <- read.csv(here("data", "Support_democracy_ajps.csv"))
sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))

@@

```{r cls-uncertainAJPSfull}
result_clsUncertainFull <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r dcpo-uncertainAJPSfull}
result_dcpoUncertainFull <- map(ls_mod_ajpsDCPO, function(aMod){ # reading a model
  result <- map(dcpo_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r coefName-AJPS, eval=TRUE}
index_coefName <- c(
  `plm::lag(Libdem_VD, 1:2)1` = "Democracy[t-1]",
  `plm::lag(Libdem_VD, 1:2)2` = "Democracy[t-2]",
  `plm::lag(Vdem_libdem, 1:2)1` = "Democracy[t-1]",
  `plm::lag(Vdem_libdem, 1:2)2` = "Democracy[t-2]",
  `plm::lag(SupDem_trim, 1)` = "Support[t-1]",
  `plm::lag(theta_trim, 1)` = "Support[t-1]",
  `plm::lag(SupDem_Democ, 1)` = "Support[t-1](demo~only)",
  `plm::lag(SupDem_Autoc, 1)` = "Support[t-1](auto~only)",
  `plm::lag(theta_dem_trim, 1)` = "Support[t-1](demo~only)",
  `plm::lag(theta_aut_trim, 1)` = "Support[t-1](auto~only)",
  `plm::lag(lnGDP_imp, 1)` = "Log~GDP~per~capita[t-1]",
  `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP~per~capita[t-1]",
  `plm::lag(GDP_imp_grth, 1)` = "GDP~per~capita~growth[t-1]",
  `plm::lag(mdprgdp_grwth, 1)` = "GDP~per~capita~growth[t-1]",
  `plm::lag(Libdem_regUN, 1)` = "Regional~democracy[t-1]",
  `plm::lag(Region_libdem, 1)` = "Regional~democracy[t-1]",
  `plm::lag(Pr_Muslim, 1)` = "Percent~Muslim[t-1]",
  `plm::lag(muslism_prop_2010, 1)` = "Percent~Muslim[t-1]",
  `plm::lag(Res_cp_WDI_di, 1)` = "Resource~dependence[t-1]",
  `plm::lag(dependence_pc_di, 1)` = "Resource~dependence[t-1]"
)
```

```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=7, fig.height=10, fig.align='center', eval=TRUE}

result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))

type_model <-
  c("Claassen 2019", "Claassen Uncertainty", "DCPO Uncertainty")

result_ajpsPooled <-
  list(result_cls,
       result_clsUncertainFull,
       result_dcpoUncertainFull) %>%
  map2_df(type_model, ~ {
    .x$pooled[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Pooled")

result_ajpsRegime <-
  list(result_cls,
       result_clsUncertainFull,
       result_dcpoUncertainFull) %>%
  map2_df(type_model, ~ {
    .x$`pooled-regime`[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Regime Specified")

df_plot <- bind_rows(result_ajpsPooled, result_ajpsRegime) %>% 
    mutate(term = index_coefName[term],
           term = factor(term, levels = unique(index_coefName)))

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: Liberal Democracy (Vdem)") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
    # Using expressions of underscore and greek letters
    scale_color_gb(palette = "digitMixed") +
    facet_wrap(~ type)

@@

saveRDS(result_clsAPSR, file = here("output", "estimates_clsMeanAPSR.RDS"))
```

@@

```{r cls-uncertainAPSRfull}
result_clsFullUncertainAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(cls_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

saveRDS(result_clsFullUncertainAPSR, file = here("output", "estimates_clsFullUncertainAPSR.RDS"))
```

@@

```{r dcpo-uncertainAPSRfull}
result_dcpoUncertainAPSR <- map(ls_mod_apsrDCPO, function(aMod){ # reading a model
  result <- map(dcpo_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

saveRDS(result_dcpoUncertainAPSR, file = here("output", "estimates_dcpoUncertainAPSR.RDS"))
```

@@

```{r coefName-APSR, eval=TRUE}
index_coefName <- c(
    `plm::lag(SupDem_trim, 1:2)1` = "Support[t-1]",
    `plm::lag(SupDem_trim, 1:2)2` = "Support[t-2]",
    `plm::lag(theta_trim, 1:2)1` = "Support[t-1]",
    `plm::lag(theta_trim, 1:2)2` = "Support[t-2]",
    `diff(Liberal_z, lag = 1)` = "Delta~Support(demo~only)",
    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Support(demo~only)",
    `plm::lag(Liberal_z, 1)` = "Support[t-1](demo~only)",
    `plm::lag(Vdem_liberal_z, 1)` = "Support[t-1](demo~only)",
    `diff(Polyarchy_z, lag = 1)` = "Delta~Support(auto~only)",
    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Support(auto~only)",
    `plm::lag(Polyarchy_z, 1)` = "Support[t-1](auto~only)",
    `plm::lag(Vdem_polyarchy_z, 1)` = "Support[t-1](auto~only)",
    `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `diff(Vdem_libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
    `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",
    `diff(lnGDP_imp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `diff(lg_imp_mdpgdp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `plm::lag(lnGDP_imp, 1)` = "Log~GDP[t-1]",
    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]"
)
```

```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on Public Support", fig.width=7, fig.height=10, eval = TRUE}
result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_clsFullUncertainAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
result_dcpoUncertainAPSR <- readRDS(here("output", "estimates_dcpoUncertainAPSR.RDS"))

type_model <-
  c("Claassen 2020", "Claassen Uncertainty", "DCPO Uncertainty")

result_apsrPooled <-
  list(result_clsAPSR,
       result_clsFullUncertainAPSR,
       result_dcpoUncertainAPSR) %>%
  map2_df(type_model, ~ {
    .x$pooled1[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Pooled")

result_apsrRegime <-
  list(result_clsAPSR,
       result_clsFullUncertainAPSR,
       result_dcpoUncertainAPSR) %>%
  map2_df(type_model, ~ {
    .x$`pooled-regime1`[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Regime Specified")

df_plot <- bind_rows(result_apsrPooled, result_apsrRegime) %>% 
    mutate(term = index_coefName[term],
           term = factor(term, levels = unique(index_coefName)))

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: Public Support for Democracy") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
    # Using expressions of underscore and greek letters
    scale_color_gb(palette = "digitMixed") +
    facet_wrap( ~ type)

@@

```{r num-cls2020a, results='asis'}
tb_result_cls <- map(result_cls, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-cls2020aUncertain, results='asis'}
tb_result_clsUncertain <- map(result_clsUncertain, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-cls2020aDCPO, results='asis'}
tb_result_DCPO <- map(result_dcpoUncertain, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-cls2020b, results='asis'}
tb_result_clsAPSR <- map(result_clsAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@

```{r num-cls2020bUncertain, results='asis'}
tb_result_clsUncertainAPSR <- map(result_clsUncertainAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@

```{r num-cls2020bDCPO, results='asis'}
tb_result_dcpoAPSR <- map(result_dcpoAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@

```{r plot-fullpackAJPS, fig.cap= "The Effect of Public Support on Democracy", fig.width=7.5, fig.height=10, eval=TRUE}

@@

```{r plot-fullpackAJPSfull, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7, eval=TRUE}

@@

```{r plot-fullpackAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO", fig.width=7.5, fig.height=10, eval=TRUE}

result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
result_dcpoUncertainAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$pooled1[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$fd1[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$pooled2[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd2 <- bind_rows(
  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$fd2[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$`pooled-regime1`[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$`fd-regime1`[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_ecmReg2 <- bind_rows(
  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$`pooled-regime2`[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg2 <- bind_rows(
  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$`fd-regime2`[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

```{r plot-fullpackAPSRfull, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10, eval=TRUE}
